\papertitle

### 2013-02-05 manuscript.tex
some section 3 edits

The literature on cooperative control of MAVs is similarly limited to larger
vehicles or analytical explorations. Hyams et al., Jung et al. and Nebot et
al. all demonstrated cooperative visual servoing for heterogeneous
UGVs~\cite{Hyams1999Cooperative}\cite{Jung1998Range}\cite{Nebot2003Agents}.
Luo, et al. and Mehta, et al. analyze UAV-UGV cooperation from a modeling
perspective~\cite{Luo2011Air}\cite{Mehta2006Adaptive}. Rudol et al.
demonstrated a similar cooperative visual servoing system with UGVs and
MAVs~\cite{Rudol2008Micro}, but the vehicles used were orders of magnitude
larger than the lightweight systems we target, and so were able to take
advantage of high-performance processors and specialized cameras. Stirling et
al. describe a method for guiding quadrotors, designated as explorers, though
a network of stationary quadrotors, designated as beacons, through an indoor
environment~\cite{SwarmStirling}. The beacons provide external sensing for
navigating the explorers through the environment, and the network can be
extended by using explorers as beacons in undiscovered areas. Their
implementation relies solely on local sensing, although our size range
requires that the actual environment sensing be external to the MAV.

@@

We initialize the particles 
uniformly across the frame before tracking begins. To improve numerical 
stability, we normalize the weights of all particles on each iteration, and 
only resample the particle population when the mean particle weight falls 
below a pre-determined threshold. 
%............................................................................%
\subsubsection{Motion Model}
Our motion model (Equation~\ref{eq:motion_model}) is a simple Gaussian transition 
centered around each particle's current position, augmented with an 
$\epsilon$-random uniform sampling strategy. In Equation~\ref{eq:motion_model}, 
$x^{[i]}_t$ is the position of the $i^\text{th}$ particle in pixel space at 
time $t$, $\Sigma$ is a chosen covariance matrix, and $b$ is a vector of the 
bounds of the pixel space.
\begin{equation}
\label{eq:motion_model}
x^{[i]}_t \sim \begin{cases}
\mathcal{N}(x^{[i]}_{t-1}, \Sigma), &\text{with probability } 1-\epsilon \\
\mathcal{U}(0,b),& \text{with probability } \epsilon \\
\end{cases}\\
\end{equation}
In the experiments we present in this work, we used a diagonal covariance matrix 
with a variance of 256, and an $\epsilon$ of 0.3. We find the Gaussian 
transition model is sufficient for tracking motion in which frame-to-frame 
position changes are relatively small. The $\epsilon$-random uniform 
transitions increase tracking robustness, by forcing the filter to always 
sample broadly across the pixel space. This helps prevent overconfidence 
and collapse, and decreases reacquisition delay.

%............................................................................%
\subsubsection{Emission Model}
Our emission model (Equation~\ref{eq:emission_model}) implements a sampling
approach to motion tracking via na\"{i}ve background subtraction, e.g. frame 
differencing~\cite{Ahad2011Computer}. On each iteration, the system provides the emission 
model with $f_0$, the frame representing the background, and $f_t$, the most 
recent frame captured. The model assigns a weight $w^{[i]}_t$ to each 
particle $x^{[i]}_t$, proportional to the color distance in RGB space 
between the pixels of $f_0$ and $f_t$ at the location $x^{[i]}_t$.
\begin{equation}
\label{eq:emission_model}
w^{[i]}_t = 1 + \norm{f_0(x^{[i]}_t)-f_t(x^{[i]}_t)}^2
\end{equation} 
Hence, particles are more likely to be resampled in regions of 
the image which are dissimilar in color from the background.

>>>>

The literature on cooperative control of MAVs is similarly limited to larger
vehicles or analytical explorations. Hyams et al., Jung et al. and Nebot et
al. all demonstrated cooperative visual servoing for heterogeneous
UGVs~\cite{Hyams1999Cooperative}\cite{Jung1998Range}\cite{Nebot2003Agents}.
Luo, et al. and Mehta, et al. analyze UAV-UGV cooperation from a modeling
perspective~\cite{Luo2011Air}\cite{Mehta2006Adaptive}. Rudol et al.
demonstrated a similar cooperative visual servoing system with UGVs and
MAVs~\cite{Rudol2008Micro}, but the vehicles used were orders of magnitude
larger than the lightweight systems we target, and so were able to take
advantage of high-performance processors and specialized cameras. Stirling et
al. describe a method for guiding quadrotors, designated as explorers, though
a network of stationary quadrotors, designated as beacons, through an indoor
environment~\cite{SwarmStirling}. The beacons provide external sensing for
navigating the explorers through the environment, and the network can be
extended by using explorers as beacons in undiscovered areas. Their
implementation relies solely on local sensing, although our size range
requires that the actual environment sensing be external to the MAV. Additionally, they do not consider time constraints in their planning, whereas our MAV has a minimum forward speed and turning radius.

@@

We initialize the particles 
uniformly across the frame before tracking begins. To improve numerical 
stability, we normalize the weights of all particles on each iteration, and 
only resample the particle population when the mean particle weight falls 
below a pre-determined threshold. 
%............................................................................%
\subsubsection{Motion Model}
Our motion model (Equation~\ref{eq:motion_model}) is a simple Gaussian transition 
centered around each particle's current position, augmented with an 
$\epsilon$-random uniform sampling strategy. The sampling law is as follows:\begin{equation}
\label{eq:motion_model}
x^{[i]}_t \sim \begin{cases}
\mathcal{N}(x^{[i]}_{t-1}, \Sigma), &\text{with probability } 1-\epsilon \\
\mathcal{U}(0,b),& \text{with probability } \epsilon \\
\end{cases}\\
\end{equation}
In Equation~\ref{eq:motion_model}, $x^{[i]}_t$ is the position of the $i^\text{th}$ 
particle in pixel space at time $t$, $\Sigma$ is a chosen covariance matrix, and $b$ 
is a vector of the bounds of the pixel space. The sampling method requires that, with 
probability $\epsilon$, the particle filter will choose a pixel from a uniform 
distribution of all of the pixels in the pixel space for the location of the $i^\text{th}$ 
particle. The $\epsilon$-random uniform transitions increase tracking robustness, by 
forcing the filter to always sample broadly across the pixel space. This helps prevent 
overconfidence and collapse, and decreases reacquisition delay.

In the experiments we present in this work, we used a diagonal covariance matrix 
with a variance of 256, and an $\epsilon$ of 0.3. We find the Gaussian 
transition model is sufficient for tracking motion in which frame-to-frame 
position changes are relatively small.

%............................................................................%
\subsubsection{Emission Model}
The emission model weights the particles' likelihood of containing a pixel location that is part of the H$^2$Bird. The particles with higher weights have a greater probability of being resampled. Our emission model implements a sampling
approach to motion tracking via na\"{i}ve background subtraction, e.g. frame 
differencing~\cite{Ahad2011Computer}: 
\begin{equation}
\label{eq:emission_model}
w^{[i]}_t = 1 + \norm{f_0(x^{[i]}_t)-f_t(x^{[i]}_t)}^2
\end{equation} 
On each iteration, the system provides the emission 
model with $f_0$, the frame representing the background, and $f_t$, the most 
recent frame captured. The model assigns a weight $w^{[i]}_t$ to each 
particle $x^{[i]}_t$, proportional to the color distance in RGB space 
between the pixels of $f_0$ and $f_t$ at the location $x^{[i]}_t$.
Hence, particles are more likely to be resampled in regions of 
the image which are dissimilar in color from the background.
